---
title: 'Data Structures: Linear_List'
output:
  pdf_document: default
  html_document:
    df_print: paged
---
# Lists
## Linear

----

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

## Linear List
* Linear list stores a collection of objects of a      certain type, denoted as elements of a list.
* Their two types of linear lists.
  + Stack
  + Queue

------

## Stack
* A stack is generally a data structure that operates   on the last in and first out principle. it is an     abstract data type.
* This means all data operations can be carried out    only on the last in first out principle.
* The push and pop operations are used for inserting   and deleting an element from a stack.
* A stack can be implement a stack using a list.

#### Stack example

```{r}

options(tinytex.verbose = TRUE)

stack_list <- list(1,2,3,5,7)

print('Examples are in Google Colab')


````

------

## Queue
* A queue is a linear type of data structure used to   store the data in a sequentially. The concept of     queue is based on the FIFO, which means "First in    First Out". It is also known as "first come first    severed". The queue has the two ends front and       rear. The next element is inserted from the rear     end and removed from the front end.
* We can perform the following operations in the       Queue:
  + Enqueue - The enqueue is an operation where we       add items to the queue.
  
  + Dequeue - The dequeue is an operation where we       remove an element from the queue. An element is      removed in the same order as it is inserted. If      the queue is empty, it is a condition of the         Underflow. 
  
  + Front - An element is inserted in the front end.     
  + Rear - An element is removed from the rear end.    

#### Queue example in R

```{r}
print('Examples are in Google Colab')


````



